\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{graphicx}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{chngpage}
\usepackage{wrapfig}

\begin{document}
\section{Group meeting summary}
{\LARGE 17. September}

\subsubsection{Agenda}
\begin{itemize}
	\item Revisit of group contract
	\item Time Schedule
	\item SWOT/GPIT/Collaborameter
	\item Ideation tools	
\end{itemize}
\subsubsection{Revisit of group contract}
The group decided to re-formulate the group contract to further clarify the consequences of not attending meetings and/or not meeting deadlines repeatedly. The results can be seen in the group contract.
\subsubsection{Time Schedule}
An overall time schedule was created, involving the most important dates. The schedule is very much subject to change as the order, importance and extent of many of the tasks is unknown at present time.
\subsubsection{SWOT/GPIT/Collaboratmeter}
Each member of the group filled out the collaborameter, Casper G. Olsen agreed to combine the 7 collaborameters into one, singular group collaborameter.\\
Due to lack of knowledge about the tasks the GPIT was not populated. Similarly the SWOT was postponed such that the information given by the Belbin test could be part of this.
\subsubsection{Ideation tools}
As part of the ideation process several pictures were brought to the meeting. The collection of pictures can be seen in the groups dropbox folder. Each picture was placed backside up and each group member drew a picture, saying whatever words came to mind seeing the picture. The general topic of all contributions was written down by Thomas S. Christensen, who also agreed to create an overview of the ideation process.
\end{document}