\subsection*{11. September}
\subsubsection{Agenda}
\begin{itemize}
\item Group name
\item Group logo
\item General brainstorm
\item Group contract
\item Communication infrastructure
\end{itemize}
The moderator was Nikolaj.
Everyone was present at the meeting.
The meeting took 3 hours.

\subsubsection{Group name}
Through a brainstorm it was concluded that a combination characteristics of ourselves and the robot we should work on would be appropriate.
The word flexible and international came together and formed the word interflex. 
%Should we write down all the words of our brainstorm because I(Nikolaj) think they are lost.
\subsubsection{Group logo}
The logo should represent our group as well as the robot we want to manipulate.
A logo was then derived from the idea of the pixar arm that is a part of the name.
The robot arm holds a globe to symbolize that the robot should do something that benefits the world we live in.
%or what did we say it meant??
\subsubsection{General brainstorm}
Under the brainstorm a number of directions were discussed.
\begin{description}
\item[Quality check] \hfill \\
A robot that can check the state of a construction or a product to tell people where they need to work.
\item[Welding] \hfill \\
A robot that does complex welding that on objects that is too big to handle for humans
\item[Waste] \hfill \\
A robot that sorts different kinds of waste to maximizing recycling
\end{description}
The group decided to do Waste sorting and had a brainstorm on what areas to cover
\begin{description}
\item[Localization] \hfill \\
Where is there a marked for this
\item[Profitability] \hfill \\
Where in the places there is a marked is there also a chance of making this a profitable product
\item[Sorting] \hfill \\
What should be sorted? What is there a need to be sorted.
How should it be sorted? (visualization,magnetism or conductivity)
\end{description}

\subsubsection{Communication infrastructure}
The group decided two ways of sharing data.

One is by dropbox. The files that are suitable for dropbox include pictures, files everyone should read, relevant information about the course.
Thomas (thomas.s.christensen101@gmail.com) is the administrator of the dropbox folder.

The other way is github. The report and everything that is expected to be edited is shared here.
The github page is something each member can visit publicly to view the files but must be a member to contribute to the repository.
Nikolaj (niive12@student.sdu.dk) is the administrator of the github repository.
The address is https://github.com/niive12/interflex.

In order to start the repository with a file structure a temporary document was uploaded so each member have a chance to check their settings before needing to edit the report.
