\subsection{Casper Gellert Olsen}
Like the rest of the group I am to perform a student to student teaching. My study line is energy technology and I have not really found a specific area that fits this project. I asked the group if there were any wishes for a topic from my study line I could teach about. Before I got any wishes I decided to talk about the electrical grid system, Smart Grid and wind turbines. I chose these topics because they, to some extent, affect us all.

\subsubsection{Session Topics}
I presented my presentation in a11 pages power point together with the use of the blackboard in the group room. My presentation went as follows:
\begin{itemize}
\item[¤] First a presentation of the agenda.
\item[¤] Then how the electrical system looked like in 1980 with only centralized power plants.
\item[¤] Followed by how the electrical system looked like today with a lot of decentralized power plant in combination with PV panels and wind turbines.
\item[¤] Then a little bit about how the electrical system works, like when electricity is produced it needs to be consumed.
\item[¤] Then about how the electricity production looks like today during a week and how it look like in 2025 where the amount of electricity produced on wind turbines and the fluctuations in supply that follows are a lot higher. I also showed how the price on electricity varies with the electricity production by wind turbines.
\item[¤] Then briefly about Smart Grid. Some ideas how to move some of the consumption during peak time. The meaning of prosumers. Intelligent power grid with electrical cars.
\item[¤] At last a little bit about wind turbines, mainly how they technically work.
\end{itemize}

The presentation lasted about 60 minutes, there were also a lot of questions during the presentation and a few afterwards.

\subsubsection{Evaluation}
\paragraph{Group:}~\\ The reason for all the questions during the presentation was because the session was very interesting. It was something all can relate to. They felt like I knew the stuff but I jumped around in the presentation and they could also see that I was not well prepared.
\paragraph{Own Reflections:}~\\
I made the power point presentation a bit late so I had not time to go through it by myself which was why I jumped a little bit around in the presentation and the audience clearly felt that. This is definitely not something I like, so it calls for a little improvement on my planning to avoid it in the future. The presentation took 15-20 minutes longer than intended but again it comes back to being unprepared. Even though I was a little unprepared I enjoyed the presentation because I felt that the entire audience was interested in the different topics. My general impressing was that the enjoyed the session even though it was of no relevance to the project.