\subsection{David}
I decide to do student to student teaching about organizational structure and hierarchy decisions, as I though about the necessity to cover this topic for a possible future need. I chose not to cover anything IT related as around half of the team has got knowledge in this topic and it was already covered by Simon.

\subsubsection{Session topics}
To cover as much as I could about hierarchy creation, I decided to start with description of key terms used in organizational structure.

Main focus was laid upon these terms:
\begin{itemize}
\item Horizontal/vertical differentiation
\item Integration
\item Centralization/decentralization
\item Organic/mechanistic structure
\item Standardization/Mutual adjustment
\item Decription of the problems arising with these terms
\item Application of these terms to our situation
\end{itemize}

\subsubsection{Evaluation}
I have been enrolled for a course about organizational structure, so I had a lot of materials to choose from, but during the presentation itself I decided not to use powerpoint as a background, which may have been a mistake. I had several problems as I had to draw tables myself, which got reflected in the evaluation.

Two of the team members noted:

"You could've used Power Point presentation as it would have been easier for you to show the tables and graphs."

"If you used presentation, you would save the time spent with drawing and could have gone into detail."

I decided not to go too much into details as it could be overwhelming for the listener and he could get confused by the amount of new terms. Instead I chose to show practical examples on hierarchy models. On the other hand by choosing not to go into detail, my presentation wasn't full 45 minutes but was something about 35 minutes including the questions and explanations on specific cases.

After the presentation I received following comments about it:

"You seem to have good knowledge about the topic, but you could've gone into more detail."

"After your presentation I feel like I have a basic overview about hierarchy creation and how to decide on the way it should be built."

"Good presentation, but it could be longer and more detailed."

\subsubsection{Summary}\
To summarize my presentation I have taken some notes for my future performances. One of them being prepared for a situation about finishing speech faster than expected and having detailed presentation. Second note is to have a Powerpoint presentation prepared if I know there will be a situation requiring a visual help like a picture, chart or graph. 
Other than that I think my presentation was well structured and the audience stayed focused and had a lot of questions about each term, which I think I was able to answer.


