\subsection{Simon}
I study IT-Engineering where you are taught skills like programming and designing software. Because the group consist of at least 3 others with knowledge within the area of programming, it would not be too interesting to teach. Therefore I decided to talk about databases and the basics of SQL to provide a view of what we are doing within IT, while being relevant to the topic of our project.

\subsubsection{Session topics}
I chose to cover the basics of database designs and why it was relevant to model before creating.
I spoke about the format of a table, the datatypes and why it could be useful to use keys when designing.
A description of when to use a DB was presented.
Followed up by a short introduction of SQL including keywords and syntax. This introduction included how to store and retrieve data. 
A few functions were mentioned to show that calculations are also possible with SQL.
A W3schools example was included to show this theory in practice. 
The presentation ended with an example of SQL Injection and how to prevent it.

\subsubsection{Evaluation}

I feel the presentation went okay, it could have used a bit more material and consistency in the explanations of topics. It is hard to teach programming to persons who do not have insight and it makes it even harder to go in depth.

I received the following comments on the presentation:

"You are good at explaining basics with the use of illustrations, even though I do not have insight in IT".

"Well structured and precise".

"A bit more of presentation length would not hurt".

"Outspoken and interesting".

So i can conclude that the material and presentation overall went good. Especially with the follow up questions about usage of a database and SQL Injection.