This section explains everything about the collaborative methods employed. 
With this, we wanted to show how different roles within the team been assigned following a specific methodology. 

The reason for introducing this section in this final report is that collaboration plays a huge role within the Experts in Teams and is one of the major activities where you get to develop skills that does not fit within the business plan. 
With the inclusion of this information, we demonstrate and justify our knowledge gained throughout this course on topics such as collaboration or idea generation. 
We decided to explain the process chronologically, which will make it easier to understand the process that we followed. 
Despite this, we saw fit to add some conclusions that relate different activities within these themes. Many choices during the process were made with the thought of these activities. 

The point of the collaboration part is also to highlight the strength and weaknesses of each member and the team as a whole to identify risks and possibilities. 
Everyone is different so you need to keep in mind when you are working in teams, how each person is and what could each member bring to the team, so it makes possible to maximize those strengths and try to fill gaps thanks to the skills of the other members.

To explain this, the content has been separated into different activities used to achieve this goal. 
This part is essential throughout the project, at first to learn about the risks, threats, etc. that the team could have and to get to know each other. 