
\subsection{Conclusion on Collaboration}

\todo [inline]{Update conclusion when Collaboration is done}
By looking at the results from the Belbin and SWOT-analysis it is not surprising that the team ended in the situation that we did. It is very clear that the team has a weakness when it comes to idea generation and as well a strength in problem solving. Prospectively it would be a good idea to look at the results from the team tests so we do not end up in the same situation as we already have.
%Vi har kæmpet længe med at finde det problem vi vil arbejde med, i projektet. Vi har brainstormet meget omkring affald, i sær e-affald men kom aldrig frem til noget brugbart. Efter at vores vejledere sagde at vi skulle til at komme videre, fik vi ændre projekt ide til en ide der er lagt lidt op til i projekt introduktionen.


We have been able to identify the potential risks and we have taken action to neutralize them. 
Since then we have gone beyond the mere fact of discovering our threats we have taken the following actions to avoid the risks:

\begin{itemize}[-]
\item We stick to a predefined business model.
\item We have created a calendar with all the deadlines.
\item We put a poster in our room with all the information about what was doing each member, so it helped us not losing the focus.
\item We used idea generating methods to obtain better results.
\item We divided the team into small groups, based on each group members interests.
\item We decided to implement the ``6 Thinking Hats'' in our discussions, so we all could think in the same way. This helped us a lot in our thinking process.
\item We have set a deadline for discussions.
\end{itemize}


But we have also taken actions that utilize our strengths to expand our potential:

\begin{itemize}[-]
\item Having many discussions that leads to solving problems and making a reality out of the ideas.
\item Dividing projects into smaller pieces so the Belbin finisher roles can be better focused. 
% \item Know when the implementer roles will kick in. Usually when the project has been financed, so their role can be a part of selling this project.
% This is just wrong - Nikolaj
\end{itemize}
