

\subsection{Reflections on Use of the Group Contract}

A copy of the group contract is to be found in appendix \ref{app:groupContract}

In this group, we have different experienceses with groupwork, some more positive than others, but we all agreed that we wanted to take this project seriously. For this reason we found the group contract redundant. 
The main points we decided to put into the contract was that everyone had to show up on time for group meetings, or at least let the group know they were late. We also decided on an agenda for group meetings. The consequence of not following the rules are that a warning will be given, and if no improvement a second warning could kick you out of the group. 

This is a sensible group contract if everyone is serious and commited to the project, but then it is redundant anyway. It was decided in the group that this was good enough for us. 

Throughout this project we have had problems communicating and getting everyone to attend. The meetings have been weakly defined and chaotic. 
Looking back, we should have been much more specific in making the group contract. It should have had more concrete consequences to be late to a meeting, or to not meet deadlines. There should also have been a guideline to figure out who should write the summeries of the group meethings, etc. 

One thing that could have helped was to have a system where if you are late, you pay a fee, or bring cake or something. This would give the small violations of the rules a small consequence. 
For the group meetings, it would have been a good idea to have a group leader and a secretary, so there was always someone who made sure to follow the agenda, and someone who wrote everything down. This could be either changing from each meeting or different people every time. A good idea would be to use the Belbin profiles to choose who should have which roles. 

Other details, like which programs the report should be written in, and which programs should be used to store it, could also have been added, to avoid any confusion. 

In hindsight, stating a more concise group contract, and following it, could have benefitted the group.