\subsection{Action and Development Plan}
\label{sec:actionDevelopmentPlan}
This plan will define the objectives, policies and the actions that will be taken the first 3 year period.
Devising an appropriate action and development plan is crucial in order to provide the team with a clear direction in the process.
Additionally it will assist in dealing with issues that lay beyond the control of the team.

%Without an appropriate Strategic Plan, it is easy to find with excesses of contingency, an absence of a measure to control the real success or failure of an administration or lack of criteria for deciding new investments and expenses to carry and control.

\subsubsection{Mission}
Interflex strives to assist companies in achieving ever greater flexibility in the welding process in their production line.
We continuously review our services to ensure that we always provide the best possible solution for our customers.
Mutual cooporation between users of our product and Interflex allows us to always develop towards increasing the efficiency of our product.

% \subsubsection{Goals}
% In section \ref{sec:managementOrganization} the key activities of interflex were listed. Below is an in depth view of each activity and the milestones within them.
% \begin{enumerate}
% \item Department of marketing. 
%       Greater participation and market consolidation in Danish market, through actions that would achieve differentiation welding robots such as high-value and useful products.
% \item Department of financial management. 
%       Purchase accounting software that helps to control and order of financial records, to minimize the waiting time for results or statistical data and financial statements of the company.
% \item Management area. Design an organizational plan that contributes to the development and implementation of all activities, operations and business goals by generating an essential 	      control tool for timely decision making.
% \item Department of services, repair and maintenance. Better manage service plans for a set period, which will allow the company to increase profitability according to business
%       requirements.
% \end{enumerate}


\subsubsection{Tactical Plan}
After defining the key activities in section \ref{key_activities}, it is necessary to think about the tactics needed to ensure that the project is successful.
Tactics for securing our position within the market as a new company will also be considered.
% These tactics are developed with the key activities from section \ref{sec:managementOrganization} in mind.

\begin{itemize}
\item \textbf{Search Funds:} To assist in securing funding of our project a strong sales pitch will be created to reach out to possible investors.
	%At the same time the company must make use of the risks, which are possible to occur and be ready to take countermeasures, if the said tactic would not turn out to be successful.
\item \textbf{Development:} Development tactics can be split into three parts. 
Firstly, the focus will be mainly on developing of the software part as it is the least financially demanding part of the development. 
During programming, hardware has to be acquired to be able to start testing as soon as the initial part of the software development is finished. 
It is also important to consider the time required for the testing part, which might be even larger than the programming itself. 
Secondly, during the first period, a contact must be made with a machinist that is capable of manufacturing the housing.
Thirdly, upon completion of the software development, work can begin on producing a working prototype.
\item \textbf{Distributors:} The main focus will be laid upon major distributors present on the market as these companies have the highest probability of having the customer base that we aim our product at.
\item \textbf{Production:} A sufficient work space for assembly that can accommodate the needs of the team, will be found. Proper accommodations will help ensure that the quality of the product is kept to the expected standards that Interflex aspires to provide.
\item \textbf{Maintenance:} After securing workers to do the assembly process, team members involved in the programming process should fully focus on maintaining the software part of the product to be able to react as quickly as possible to flaws and/or bugs reported by customers. Taking swift action against flaws help keep a positive image of the company and its product. Other members of the team should focus on compatibility expansion to attract a wider spectrum of customers and ensure faster revenue generation.
\end{itemize}


% Once we have defined all our goals and tactics in a medium to long term, it is time to design the tactical plan. To do this we must make a projection of current activities and development, and make a prognosis and planning of new programs and business operations for the future. At this stage we will define the objectives, tactics, programs and budgets that will conduct the company. This is process by which detailed plans are carried out, taking into account the development of resources for Strategic Planning.

% \paragraph*{Objectives}~\\
% Our objectives in the medium-short term (a year approx) will be the next ones:
% \begin{itemize}[-]
% \item Get funding to create and start developing the company.
% \item Develop the capacity to compete in the marketplace technology.
% \item Consolidate the company through the support of our main customer, Valk Welding.
% \end{itemize}

% \paragraph*{Tactical programs}~\\
% 
% \begin{enumerate}
% \item Marketing program.
%       Challenge the national market with products of the company.
% \item Production program.
% 	Develop and implement the technology needed to obtain the final product.
% 	This is a plan for the first year, so this is what we are looking for. 
% 	Next years we will have different problems in this area, but right now, we should focus on developing the product. 
% 	We will have time to optimize the production process during the next years, but first we need to have the product.
% \item Staff development program
% 	Train the staff in order to be able to develop all our processing plan.
% 	As it is a new technology, we must train operators to be capable of working with the necessary machinery.
% \item Financial program.
%       Funding and reduce costs.	
% \end{enumerate}


% \paragraph*{Tactics and costs}~\\
% \begin{enumerate}
% \item In order to challenge the national market, we are going to make a market analysis to know what exactly they are looking for. We are going to call them and see what they need, so we can modify our robot in a future. It also will help Valk Company to sell our robots, if we show them our result of our market analysis.
% \item Valk Comapany will provide us some training courses for the operators who need training on advanced programming about welding.  
% \end{enumerate}
