\subsubsection{Development Plan}
\paragraph*{First Year}~\\
To get an overview of the software development an estimate of the complexity of each sub problem was made.
Then each task was considered for the potential for group work.
We have a constraint of 3 programmers in the group.
Adding more people to a task doesn't always make the task easier to solve so we decided to make estimates based on the programmers we have in the group.
Since the hardware testing is crucial to the software development we have put this together with the software development plan. 
We have plotted a Gantt chart over the software development and the hardware development in figure \ref{development_gantt}.
The development is being done by dividing our team into three groups. 

The first group will be responsible for the software. 
This group will implement the functionality that is required.

The second group will be responsible for the hardware. 
They will be making the designs and planning what test should the sensor be able to pass.

The third group will be responsible for marketing. 
We need someone to be in charge of getting contacts and funding. 

We need to develop the control software that allows us to control the robot using the sensors chosen for the tool. 

While the first parts of the control software is being developed we need a source of funding.
In order to develop this successfully the rest of the team relies on the group responsible for getting funding for the initial year.
Investing in our company this early will impose a large risk, so finding an investor that is willing to pay may be harder early on in the project. 
If we get a loan in a bank we are not likely to get a low interest, but right now this is the assumption used in the budget.
When we have funding for the first year we can look for customers that are willing to sell our products and help them with integrating our product in their line of products.

The testing phase depends on the control software and the funding. 
During the testing phase we will have to go back and add functionality to the control software. 
While a part of our team is working on the testing the software team will make the interface.

The time estimates of the complexity can be found in appendix \ref{app:software_development_time}.
We have estimated the time to develop the software to 51.5 weeks.

\begin{figure}[ht]
\centering
\begin{tabular}{ll}
Week                        &\begin{tikzpicture}[scale=\ganttScaling] \node at (0,0) {0}; \foreach \x in {1,...,5} \node at ({\x * 10},0) {\x0};  \end{tikzpicture}\\
\multicolumn{2}{l}{\textbf{Control Software}}\\
% Laser range                 &\begin{tikzpicture}[scale=\ganttScaling] \draw[line width=2mm,color=blue!50] (0,0) ( 0.00,0)  --    ++(  0.27,0);  \end{tikzpicture}\\
Laser range                                          &\ganttLine{blue!50} {  0.00 }{  0.27 }\\
UV-flash                                             &\ganttLine{blue!50} {  0.00 }{  0.27 }\\
Camera                                               &\ganttLine{blue!50} {  0.00 }{  2.16 }\\     
OpenCV                                               &\ganttLine{blue!50} {  2.16 }{  6.08 }\\     
Planning                                             &\ganttLine{blue!50} {  8.24 }{  4.05 }\\     
Generate program                                     &\ganttLine{blue!50} { 46.08 }{  5.41 }\\ %51.49
\multicolumn{2}{l}{\textbf{Software for interface}}\\                              
Pistol angle                                         &\ganttLine{blue}    { 12.30 }{  2.70 }\\
Metal type                                           &\ganttLine{blue}    { 12.30 }{  2.70 }\\
Metal thickness                                      &\ganttLine{blue}    { 12.30 }{  2.70 }\\
Communication                                        &\ganttLine{blue}    { 15.00 }{  2.70 }\\
\multicolumn{2}{l}{\textbf{Hardware design}}\\                                                        
Design (CAD)                                         &\ganttLine{red}     {  0.00 }{  4.05 }\\
Testing                                              &\ganttLine{red}     { 12.30 }{ 20.27 }\\
Functional prototype                                 &\ganttLine{red}     { 32.57 }{ 13.51 }\\ %46.08
\multicolumn{2}{l}{\textbf{Marketing}}\\                                                        
Find funding                                         &\ganttLine{purple}  {  0.00 }{ 12.30 }\\
Get contract with sellers                            &\ganttLine{purple}  { 12.30 }{ 15.70 }\\
\parbox[t]{3cm}{Help sellers convince early adopters}&\ganttLine{purple}  { 28.00 }{ 18.08 }\\ %46.08
\end{tabular}
\caption{Time table for development the first year}
\label{development_gantt}
\end{figure}

\paragraph*{Second Year}~\\
The second year is where we start making products. 
To keep cost down we will assemble the sensors ourselves. 
This allows us to continue the development when there is no orders and we can see how the sensors is received by SME's.
As the market is small we have to be ready for making customer specific improvements to satisfy the end users.
This will create an income that will allow us to repay the debt we have created the first year.
Our goal is to improve the product on a customer by customer case until it has the features that the rest of the market needs.

\paragraph*{Third Year}~\\
Now our product should be ready for everyone and we have an established place in the market. 
We are selling more products and we have to hire more people to be able to have a development team as well as delivering on all orders.
Now our goal is to expand the features of our sensor so it is usable for even more end users.
This will be done by getting more customers so we can sell to a different segment. 
This might involve another type of robot so the Generate Program functionality needs to be rewritten so it works for other robots.
