\begin{document}

\section{Idea and background}
This section briefly covers a description of the problem that we are trying to solve, how we are going to solve it, which customers that could have an interest in it and how we would benefit from it and create profit.

Also it will contain a short presentation of the team and why we are the perfect fit for this start up company.

\subsection{Problem}
Basically the problem involves flexibility within the area of industrial processing. Reprogramming robots is common when a new task is up and within the field of robotic welding it is often required to do so. Usually these movement coordinates of a welding robot is stored in recipes, but those cannot handle new tasks. Adaptability and precision is the major key words when it comes to welding tasks for industrial robots.

\subsection{Solution}
We provide a solution to the problem mentioned above, which do not require programming. The product itself is an add-on for welding robots, that allows the robot to detect the areas to weld by itself. The add-on will provide coordinates, used to create a welding-path for the robot. 

The product consists of a micro computer, which is used to make  calculations based on input from a camera and a laser range scanner. 

\subsection{Customer}
Relevant customers are companies who are already in the zone of robotic welding, companies who could be interested in investing or buying the particular idea. Primarily it will be customers who develop either robots or other technical parts for them.  

\subsection{Revenue}
Revenue is generated through start up investments from stakeholders. When the product is released, we are open for selling our part of the idea or patent. 

\subsection{People}


\subsection{Passion}


\end{document}