\section{Appendix: Pricing of Tool}
For the success of this product it is crucial that the price stays competitive. Offline programming methods currently in use today\footnote{Information courtesy of Valk Welding} costs 100.000Dkk for the software and required training. Our product should stay within this budget or offer significant advantages over competition.
\subsection{Bill of Materials}
In figure \ref{tab:BoM} is a rough estimate of the budget for each component needed to produce the robot. All of the prices are based on average costs of typical industrial range products in each category.  
\begin{figure}[H]
	\begin{center}
		\begin{tabular}{l c r}
		Product            & & Budget (DKK)\\
		\hline
		Camera 				& : & 5.000  \\
		Laser scanner		& : & 5.000 \\
		Custom Housing		& : & 5.000\\
		Embedded Hardware	& : & 2.000\\
		Software/Firmware	& : & 5.000\\
		UV flash			& : & 2.000\\
		Interface			& : & 3.000\\
		Marker				& : & 500\\[0.2cm]
		\hline
		Total				& : & 28.500\\ 
		\end{tabular}
	\end{center}
	\caption{Estimated bill of materials}
	\label{tab:BoM}
\end{figure}
Some of the components mentioned in figure \ref{tab:BoM} require some elaboration:
\paragraph{Custom Housing:}
As previously mentioned most of the components used to manufacture this product already exist, making the manufacturing of the product mostly an assembly. However, a custom housing to hold the components as well as protect them from the potentially harsh conditions of a welding environment must be made. A design will be made inhouse and a machine shop [Real name?] will be hired to manufacture the housing.
\paragraph{Embedded Hardware:}
In order to provide the robot with the necessary information to perform a quality weld, it is necessary to include some hardware for managing the image processing as well as a range of other tasks. There are many off-the-shelf [off/of?] solutions on the market today, one of which is expected to meet the processing-needs of our application. If this is not the case or if it is economically advantagous, a custom processing board will be developed, in either case the assumed maximum budget is unaltered.
\paragraph{Software/Firmware:}
In order to realise this product a multitude of different programming tasks must be completed, naturally, the development costs must be included in the final price of the product.
\subsection{Manufacturing Cost}
Having bought all of the parts it is still necessary to assemble, test and paint each product. It will take an estimated 100 \todo[inline]{how many hours was it? 73?} manhours from parts to final product. Working at an engineers minimum wage this translates to 12.000Dkk.\todo[inline]{verify}
\subsection{Final Cost}
Taking into account both the BoM and the manufacturing cost, the total expenses of manufacturing the product reaches 40.500Dkk. \todo[inline]{Should we conclude on the final cost (80000) here? it seems malplaced..}