\subsubsection{Software development plan}
To get an overview of the software development an estimate of the complexity of each sub problem was made.
Then each task was considered for the potential for group work.
We have a constraint of 3 programmers in the group.
Adding more people to a task doesn't always make the task easier to solve so we decided to make estimates based on the programmers we have in the group.
Since the hardware testing is crucial to the software development we have put this together with the software development plan. 
We have plotted a Gantt chart over the software development and the hardware development in figure \ref{software_development_gantt}.
The development is being done by dividing our team into two groups. 
One group will be responsible for the hardware, making the designs and planning what test should the sensor be able to pass.
The other group will be responsible for the software. 
This group will implement the functionality that is required.
We need to develop the Control Software that allows us to control the robot using the the sensors we have picked. 
When the Control Software is created we can start the testing phase. 
During the testing phase we will have to go back and add functionality to the Control Software. 
While a part of our team is working on the testing the software team will make the interface.
The Hardware team is responsible for 
The time estimates of the complexity can be found in appendix \ref{app:software_development_time}.
We have estimated the time to develop the software to 51.5 weeks.
\nikolaj{I have not created the appendix with the timing yet... maybe it should be a large table with all our timing estimates or something}

\begin{figure}[ht]
\centering
\begin{tabular}{ll}
Week                        &\begin{tikzpicture}[scale=\ganttScaling] \node at (0,0) {0}; \foreach \x in {1,...,5} \node at ({\x * 10},0) {\x0};  \end{tikzpicture}\\
\multicolumn{2}{l}{\textbf{Control Software}}\\
% Laser range                 &\begin{tikzpicture}[scale=\ganttScaling] \draw[line width=2mm,color=blue!50] (0,0) ( 0.00,0)  --    ++(  0.27,0);  \end{tikzpicture}\\
Laser range                 &\ganttLine{blue!50}      {  0.00 }{  0.27 }\\
UV-flash                    &\ganttLine{blue!50}      {  0.00 }{  0.27 }\\
Camera                      &\ganttLine{blue!50}      {  0.00 }{  2.16 }\\     
OpenCV                      &\ganttLine{blue!50}      {  2.16 }{  6.08 }\\     
Planning                    &\ganttLine{blue!50}      {  8.24 }{  4.05 }\\     
Generate program            &\ganttLine{blue!50}      { 46.08 }{  5.41 }\\
\multicolumn{2}{l}{\textbf{Software for interface}}\\                                   
Pistol angle                &\ganttLine{blue}         { 12.30 }{  2.70 }\\
Metal type                  &\ganttLine{blue}         { 12.30 }{  2.70 }\\
Metal thickness             &\ganttLine{blue}         { 12.30 }{  2.70 }\\
Communication               &\ganttLine{blue}         { 15.00 }{  2.70 }\\
\multicolumn{2}{l}{\textbf{Hardware design}}\\                                                             
Design (CAD)                &\ganttLine{red}          {  0.00 }{  4.05 }\\
Testing                     &\ganttLine{red}          { 12.30 }{ 20.27 }\\
Functional prototype        &\ganttLine{red}          { 32.57 }{ 13.51 }\\
\end{tabular}
\caption{Time table for software development plan}
\label{software_development_gantt}
\end{figure}
